### 2014-07-21 Docs/managing_jobs/managingjobs.tex
update the edison run info

gfortran is probably the best compiler for \maestro.  Here are some
version-specific notes:

@@

The submission script {\tt jaguar.run} and shell script
{\tt process.jaguar} in {\tt Util/job\_scripts/jaguar/}
are designed to allow you to run \maestro\ with minimal interaction,
while being assured that the data is archived to HPSS on the NCCS
machines.

To use the scripts, first create a directory in HPSS that has the same
name as the directory on lustre you are running in (just the directory
name, not the full path).  E.g.\ if you are running in a directory
call {\tt wdconvect\_run}, then do:
\begin{verbatim}
hsi
mkdir wdconvect_run
\end{verbatim}
(Note: if the hsi command prompts you for your password, you will need to
talk to the NCCS help desk to ask for password-less access to HPSS).

The script {\tt process.jaguar} is called from {\tt jaguar.run} and
will run in the background and continually wait until checkpoint or
plotfiles are created (actually, it always leaves the most recent one
alone, since data may still be written to it, so it waits until there
are more than 1 in the directory).

@@

The {\tt jaguar.run} submission script has code in it that will look
at the most recently generated checkpoint files, make sure that they
were written out correctly (it looks to see if there is a Header file,
since that is the last thing written), and automatically set the {\tt
  --restart} flag on the run line to restart from the most recent
checkpoint file.  This allows you to job-chain a bunch of submission
and have them wait until the previous job finished and then
automatically queue up:
\begin{verbatim}
qsub -W depend=afterany:<JOB-ID>  <QSUB SCRIPT>
\end{verbatim}
where {\tt <JOB-ID>} is the id number of the job that must complete
before the new submission runs and {\tt QSUB SCRIPT} is the submission
script (e.g.\ {\tt jaguar.run}).
This way you can queue up a bunch of runs and literally leave things
alone and it will restart from the right place automatically and store
the data as it is generated.

When {\tt process.jaguar} is running, it creates a lockfile (called
{\tt process.pid}) that ensures that only one instance of the script
is running at any one time.  Sometimes if the machine crashes, the
{\tt process.pid} file will be left behind, in which case, the script
aborts.  Just delete that if you know the script is not running.

@@

@@

hopper is configured with 24 cores per node, with the cores grouped
into 4 NUMA nodes of 6 cores each.  Best performance is seen when
running with 6 threads and 4 MPI tasks per node, using the following
run line:
\begin{verbatim}
aprun -n 128 -N 4 -d 6 -S 1 -ss ./main.Linux.Cray.mpi.omp.ex inputs_3d
\end{verbatim}
Here, {\tt -n} is the number of MPI tasks, and {\tt n * d} is the
total number of cores (which should match the {\tt mppwidth} set at
the top of the submission script). \\

\noindent (2013-01-15) It's been seen that sometimes an MPICH2 error is 
generated of the form:
\begin{verbatim}
MPIU_nem_gni_get_hugepages(): Unable to mmap 8388608 bytes for file 
/var/lib/hugetlbfs/global/pagesize-2097152/hugepagefile.MPICH.1.19467.kvs_14619732, 
err Cannot allocate memory
\end{verbatim}
Setting:
\begin{verbatim}
export MPICH_GNI_MALLOC_FALLBACK=enabled
\end{verbatim}
in your submission script seems to fix this issue.  This will allow
MPI to continue if there are insufficient huge pages in one NUMA node.
(Alternately, it was suggested to run without the {\tt -ss} option to
{\tt aprun}.

@@

The same set of submission scripts are available for hopper at NERSC in 
{\tt Util/job\_scripts/hopper/}.  They are mostly identical, with a few
minor changes for the local system configuration.  The use is the same
as described above.

>>>>

gfortran is probably the best-supported compiler for \maestro.  Here are some
version-specific notes:

@@

The submission script {\tt titan.run} and shell script
{\tt process.titan} in {\tt Util/job\_scripts/titan/}
are designed to allow you to run \maestro\ with minimal interaction,
while being assured that the data is archived to HPSS on the OLCF
machines.

To use the scripts, first create a directory in HPSS that has the same
name as the directory on lustre you are running in (just the directory
name, not the full path).  E.g.\ if you are running in a directory
call {\tt wdconvect\_run}, then do:
\begin{verbatim}
hsi
mkdir wdconvect_run
\end{verbatim}
(Note: if the hsi command prompts you for your password, you will need to
talk to the OLCF help desk to ask for password-less access to HPSS).

The script {\tt process.titan} is called from {\tt titan.run} and
will run in the background and continually wait until checkpoint or
plotfiles are created (actually, it always leaves the most recent one
alone, since data may still be written to it, so it waits until there
are more than 1 in the directory).

@@

The {\tt titan.run} submission script has code in it that will look
at the most recently generated checkpoint files, make sure that they
were written out correctly (it looks to see if there is a Header file,
since that is the last thing written), and automatically set the {\tt
  --restart} flag on the run line to restart from the most recent
checkpoint file.  This allows you to job-chain a bunch of submission
and have them wait until the previous job finished and then
automatically queue up:
\begin{verbatim}
qsub -W depend=afterany:<JOB-ID>  <QSUB SCRIPT>
\end{verbatim}
where {\tt <JOB-ID>} is the id number of the job that must complete
before the new submission runs and {\tt QSUB SCRIPT} is the submission
script (e.g.\ {\tt titan.run}).
This way you can queue up a bunch of runs and literally leave things
alone and it will restart from the right place automatically and store
the data as it is generated.

When {\tt process.titan} is running, it creates a lockfile (called
{\tt process.pid}) that ensures that only one instance of the script
is running at any one time.  Sometimes if the machine crashes, the
{\tt process.pid} file will be left behind, in which case, the script
aborts.  Just delete that if you know the script is not running.

@@

{\em Note: this information may be out-of-date.}

@@

edison is configured with 24 cores per node split between two Intel IvyBridge
12-core processors.  Each processor connects to 1/2 of the node's memory
and is called a NUMA node, so there are 2 NUMA nodes per edison node.
Best performance is seen when
running with 6 threads and 4 MPI tasks per node, as example:
\begin{verbatim}
aprun -n 192 -N 4 -S 2 -d 6 -ss ./main.Linux.Cray.mpi.omp.exe inputs_3d
\end{verbatim}
Here,
\begin{itemize}
\item {\tt -S} is the number of MPI tasks per NUMA node (you want to split them
  across the 2 NUMA nodes per Edison node)
\item {\tt -n} is the total number of MPI tasks for the entire application
\item {\tt -N} is the number of MPI tasks PER Edison node
\item {\tt -d} is the number of OpenMP threads per MPI task (must match 
{\tt OMP\_NUM\_THREADS})
\end{itemize}
The product of {\tt -N} and {\tt -d} should be 24---the total number of cores
per edison node.
The script {\tt
Util/job\_scripts/edison/edison.run} provides an example.

\subsubsection{Older information---still relevant?}
\noindent (2013-01-15) It's been seen that sometimes an MPICH2 error is 
generated of the form:
\begin{verbatim}
MPIU_nem_gni_get_hugepages(): Unable to mmap 8388608 bytes for file 
/var/lib/hugetlbfs/global/pagesize-2097152/hugepagefile.MPICH.1.19467.kvs_14619732, 
err Cannot allocate memory
\end{verbatim}
Setting:
\begin{verbatim}
export MPICH_GNI_MALLOC_FALLBACK=enabled
\end{verbatim}
in your submission script seems to fix this issue.  This will allow
MPI to continue if there are insufficient huge pages in one NUMA node.
(Alternately, it was suggested to run without the {\tt -ss} option to
{\tt aprun}.

@@

The same set of submission scripts described for titan are available
for edison at NERSC in {\tt Util/job\_scripts/edison/}.  They are
mostly identical, with a few minor changes for the local system
configuration.  The use is the same as described above.

\subsection{Batch visualization using \yt}

The scripts {\tt parallel-yt} and {\tt process-edison.run} in {\tt
Util/job\_scripts/edison} show how to invoke \yt\ to loop over a 
series of plotfiles and do visualization.  A number of tasks are
run at once on the node, each operating on a separate file.  Note:
it is important that {\tt aprun} be used to launch the \yt\ script
to ensure that it is run on the compute node.
